---
title: "parse in python"
format: html
editor: source
---

## Basics

-   need to 'break apart' bps docs into parts so we can reassemble in a database
-   sections are denoted in multiple ways, mostly by **bold** which is a problem as there are bold sections in table
-   some ideas
    -   try to remove all tables then parse by bold-tables removed with Python
-   add error handling at some point
-   need to agree on and implement column naming convention, probably snake case with Janitor package
-   would be nice to have one code block for all tables, but due to variations in formatting, etc. doing each one separately

## python to remove tables

```{python}

# Specify the input and output directories
input_directory = 'test_docs/pine_oak_41_50_51/'
output_directory = 'no_tables2'



import os
from docx import Document

def remove_tables_from_docx(input_file, output_file):
    # Load the document
    doc = Document(input_file)
    
    # Find all tables in the document
    tables = doc.tables
    
    # Iterate over tables in reverse order and delete them
    for table in reversed(tables):
        table._element.getparent().remove(table._element)
    
    # Save the modified document to the output file
    doc.save(output_file)
    print(f"Tables removed and saved to {output_file}")

def process_directory(input_directory, output_directory):
    # Create the output directory if it doesn't exist
    if not os.path.exists(output_directory):
        os.makedirs(output_directory)
    
    # Iterate over all files in the input directory
    for filename in os.listdir(input_directory):
        # Process only .docx files
        if filename.endswith('.docx'):
            input_file = os.path.join(input_directory, filename)
            output_file = os.path.join(output_directory, filename)
            remove_tables_from_docx(input_file, output_file)



# Process the directory
process_directory(input_directory, output_directory)




```

**Looks like it worked!**

## Try to extract most **Bold** components to a dataframe

Components:

Vegetation Type Map Zones Model Splits or Lumps Geographic Range Biophysical Site Description Vegetation Description Disturbance Description Scale Description Adjacency or Identification Concerns Issues or Problems Native Uncharacteristic Conditions Comments

## Get specific sections in R from table-less docs

Having to ignore these sections:

-   BpS Dominant and Indicator Species
-   Fire Frequency
-   Succession Classes



```{r}
library(officer)
library(dplyr)
library(stringr)

# Define the directory path and sections
directory_path <- "no_tables2/"
sections <- c("Vegetation Type",
              "Map Zones",
              "Model Splits or Lumps",
              "Geographic Range",
              "Biophysical Site Description",
              "Vegetation Description",
              "Disturbance Description",
              "Scale Description",
              "Adjacency or Identification Concerns",
              "Issues or Problems",
              "Native Uncharacteristic Conditions",
              "Comments",
              "References")  # Added References section

# Function to extract sections from a Word document
extract_sections <- function(doc_path, sections) {
  doc <- read_docx(doc_path)
  paragraphs <- docx_summary(doc)
  
  content_list <- lapply(sections, function(section) {
    section_index <- which(paragraphs$text == section)
    if (length(section_index) == 0) return(NA)
    content <- ""
    i <- section_index + 1
    while (i <= nrow(paragraphs)) {
      if (paragraphs$text[i] %in% sections) break
      if (str_detect(paragraphs$text[i], "Succession Classes")) break
      if (str_detect(paragraphs$text[i], "BpS Dominant and Indicator Species")) {
        while (i <= nrow(paragraphs) && !paragraphs$text[i] %in% sections) {
          i <- i + 1
        }
        break
      }
      if (str_detect(paragraphs$text[i], "Fire Frequency")) {
        while (i <= nrow(paragraphs) && !paragraphs$text[i] %in% sections) {
          i <- i + 1
        }
        break
      }
      content <- paste(content, paragraphs$text[i], sep = "\n")
      i <- i + 1
    }
    content <- trimws(content)  # Trim leading/trailing whitespace
    if (content == "") return(NA)  # Return NA if the section is empty
    return(content)
  })
  
  names(content_list) <- sections
  content_list <- as.data.frame(content_list)
  content_list$document <- basename(doc_path)
  return(content_list)
}

# Get all docx files in the directory
doc_paths <- list.files(directory_path, pattern = "\\.docx$", full.names = TRUE)

# Extract data from each document
data_list <- lapply(doc_paths, function(doc_path) {
  extract_sections(doc_path, sections)
})

# Combine the data into a single dataframe
df <- bind_rows(data_list)

# Move 'document' column to the first position
text_df <- df %>% select(document, everything())

# Print the dataframe
print(df)

write.csv(text_df, file = "pieces/text_df.csv")


```

Looks pretty good!

## Extract tables and export to .csv

### Table 1: Modelers

Table 1 has Modelers (names) and Reviewers (names) headers, plus columns with emails for each. Fun.

```{r}


# Load packages
library(dplyr)
library(docxtractr)

## SET DIRECTORY AND MAKE LIST OF DOCS ------------

# Specify the directory containing the docx files
#*** kb Took ALL BpS description documents from Apex RMS git hub ref con repository:
#https://github.com/ApexRMS/landfireReferenceConditions?tab=readme-ov-file
docx_directory <- "test_docs/pine_oak_41_50_51/"

# List all docx files in the directory
docx_files <- list.files(path = docx_directory, pattern = "\\.docx$", full.names = TRUE)


## CREATE EMPTY LIST AND LOOP THROUGH ALL DOCUMENTS TO POPULATE LIST  ------------

# Initialize an empty list to store tables from each document
all_tables <- list()

# Iterate through each docx file
for (docx_file_path in docx_files) {
  # Read in the docx file
  docx_file <- docxtractr::read_docx(docx_file_path)
  
  docx_describe_tbls(docx_file)
  
  # Extract table from docx
  table_from_docx <- docx_extract_tbl(docx_file, tbl_number = 1) # CHANGE THIS FOR DIFFERENT TABLES
  
  # Get the document name dynamically
  doc_name <- tools::file_path_sans_ext(basename(docx_file_path))
  
  # Add a new column for the document name
  table_from_docx$BPS_MODEL <- doc_name
  
  # Append the table to the list
  all_tables[[doc_name]] <- table_from_docx
}

## MAKE AND WRITE THE TABLE

# Combine all tables into a single dataframe
modelers <- bind_rows(all_tables) %>%
  rename(Modeler_email = 2) %>%
  rename(Reviewer_email = 4) %>%
  select(BPS_MODEL, everything())

#*** write table 1 to .csv
write.csv(modelers, file = 'pieces/modelers.csv', row.names = FALSE)

```

### Table 2: BpS Dominant and Indicator Species

No extra work needed on this one I hope.

```{r}

## NOTES -----------
# Want to get indicator species per BpS doc
# Several docs in one directory
# BpS Dominant and Indicator Species is the specific table, which is table 2

## PACKAGES ------------

# Load the dplyr package
library(dplyr)
library(docxtractr)

## SET DIRECTORY AND MAKE LIST OF DOCS ------------

# Specify the directory containing the docx files
#*** kb Took ALL BpS description documents from Apex RMS git hub ref con repository:
#https://github.com/ApexRMS/landfireReferenceConditions?tab=readme-ov-file
docx_directory <- "test_docs/pine_oak_41_50_51/"

# List all docx files in the directory
docx_files <- list.files(path = docx_directory, pattern = "\\.docx$", full.names = TRUE)


## CREATE EMPTY LIST AND LOOP THROUGH ALL DOCUMENTS TO POPULATE LIST  ------------

# Initialize an empty list to store tables from each document
all_tables <- list()

# Iterate through each docx file
for (docx_file_path in docx_files) {
  # Read in the docx file
  docx_file <- docxtractr::read_docx(docx_file_path)
  
  docx_describe_tbls(docx_file)
  
  # Extract table from docx
  table_from_docx <- docx_extract_tbl(docx_file, tbl_number = 2) # CHANGE THIS FOR DIFFERENT TABLES
  
  # Get the document name dynamically
  doc_name <- tools::file_path_sans_ext(basename(docx_file_path))
  
  # Add a new column for the document name
  table_from_docx$BPS_MODEL <- doc_name
  
  # Append the table to the list
  all_tables[[doc_name]] <- table_from_docx
}

## MAKE AND WRITE THE TABLE

# Combine all tables into a single dataframe
indicator_species <- bind_rows(all_tables) %>%
  select(BPS_MODEL, everything())
  

#*** kb changed output location
write.csv(indicator_species, file = 'pieces/bps_indicators.csv', row.names = FALSE)
```

### Table 3: Fire Frequency

Blank cells and formatting (centered fonts) may cause issues. \*\*Looks OK, empty cells are empty and no issues with centered values.

```{r}
## PACKAGES ------------

# Load the dplyr package
library(dplyr)
library(docxtractr)

## SET DIRECTORY AND MAKE LIST OF DOCS ------------

# Specify the directory containing the docx files
#*** kb Took ALL BpS description documents from Apex RMS git hub ref con repository:
#https://github.com/ApexRMS/landfireReferenceConditions?tab=readme-ov-file
docx_directory <- "test_docs/pine_oak_41_50_51/"

# List all docx files in the directory
docx_files <- list.files(path = docx_directory, pattern = "\\.docx$", full.names = TRUE)


## CREATE EMPTY LIST AND LOOP THROUGH ALL DOCUMENTS TO POPULATE LIST  ------------

# Initialize an empty list to store tables from each document
all_tables <- list()

# Iterate through each docx file
for (docx_file_path in docx_files) {
  # Read in the docx file
  docx_file <- docxtractr::read_docx(docx_file_path)
  
  docx_describe_tbls(docx_file)
  
  # Extract table from docx
  table_from_docx <- docx_extract_tbl(docx_file, tbl_number = 3)  # CHANGE THIS FOR DIFFERENT TABLES
  
  # Get the document name dynamically
  doc_name <- tools::file_path_sans_ext(basename(docx_file_path))
  
  # Add a new column for the document name
  table_from_docx$BPS_MODEL <- doc_name
  
  # Append the table to the list
  all_tables[[doc_name]] <- table_from_docx
}

## MAKE AND WRITE THE TABLE

# Combine all tables into a single dataframe
fire_frequency <- bind_rows(all_tables) %>%
  select(BPS_MODEL, everything())
  

#*** kb changed output location
write.csv(fire_frequency , file = 'pieces/fire_frequency.csv', row.names = FALSE)
```
